Capstone Movielens Report

### 2025-11-18 reports/capstone-movielens.site/05.appendix.Rmd
Minor fix for function: `model.tune.param_range`.

Implements an algorithm for fine-tuning the model under test by figuring out the most precise value possible of the *regularization parameter* $\lambda$ over a given interval determined by the start and end values of the interval passed in the [loop_starter] argument, using the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].

>>>>

Implements an algorithm for fine-tuning the model under test by figuring out the most precise value possible of the *regularization parameter* $\lambda$ over a given interval determined by the $start$ and $end$ values of the interval passed in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument, using the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].
